\section{Main Functionalities}

The online carpet store is designed to store various types of data related to the operation of the business, including information about producers, customers, products, orders, and comments.\\
This data is essential for providing a seamless shopping experience and ensuring the privacy and security of our customers and producers.

To achieve this, the website is divided into several main sections:\\
\begin{itemize}
    \item 1. producer section: This section allows sellers to create and manage their accounts, add and edit their products, manage orders, and communicate with customers. The seller data, including the company name, username, password, email, mobile number, bank account, address, and products offered, is stored securely in the system.

    \item 2. Customer section: This section allows customers to create and manage their accounts, view their order history, and make changes to their personal information, such as their shipping address or payment method. The customer data, including the name, surname, username, password, email, mobile number, bank account, and address, is stored securely in the system.

    \item 3. Product section: This section showcases the individual products available for purchase. Each product page includes a clear photo of the product, as well as detailed product information such as size, materials, colors, price, and availability. The product data, including the name, picture, size and dimension, materials, colors, price, quantities, brand, categories, quality, and text description, is stored securely in the system.

    \item 4. Order section: This section allows customers to add products to their shopping cart, review their orders, and complete the checkout process. The checkout process is secure and easy to use, with options for payment and shipping. The order data, including the order name, number, product ID, total price, status, date, and time, is stored securely in the system.

    \item 5. Comment section: This section allows customers to leave comments and feedback on products. The comment data, including the user ID, number of replies, likes, and dislikes, is stored securely in the system.
\end{itemize}


